Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-12 appendix.tex
u
tex

	\item [HM] do we fix the anchor like ACT? | marginal. Queued.

	\item [M] difference between EST, ACT, AMD/ AMDsemi.
		Other methods (than HM) cannot effectively learn from the strongest
		adversary as the inner maximization is indirectly (and not guaranteed).
		HM follows the min-max paradigm (can be incorporated into FAT etc).
		Both ACT and HM stops at a specific point.

	\item [M] Sampling also matters in adversarial training for deep metric learning.

		[source hardness and destination hardness] different source sampling
		strategy and different destination sampling strategy. attack
		destination. DML loss not that sensitive to sampling? or generic
		advtrain method for DML? | still investigating

@@

	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)

>>>>

@@

	\item [\xmark] do we fix the anchor like ACT? | negative result observed
		on fashion-mnist (rhetrm).

	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)
		Not every triplet is useful in this regard. Not all of them have to
		contribute to the final gradient.

### 2021-10-12 robdml.tex
tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning}

@@

create adversarial
examples for increasing their hardness towards that of a harder sample triplet.
%
%
%
Triplet hardness still matters in adversarial training for deep metric
learning.

@@

% evaluation and conclusion
\oo{[experimetal evaluations]}
To validate the effectiveness of the proposed method, we conduct experiments
on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
Online Product. \oo{the results suggest that}

@@

\cite{Authors14}

>>>>

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Efficiently Enhancing Adversarial Robustness for Deep Metric Learning}

@@

@@

% evaluation and conclusion
\oo{[experimetal evaluations]}
To validate the effectiveness of the proposed method, we conduct experiments
on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
Online Product. Our conclusions are:
%
(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
based DML models.
%
\oo{the results suggest that}

@@

HM follows the min-max paradigm, (can be incorporated into FAT etc).
Both ACT and HM stops at a specific point.
